---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MHplot

<!-- badges: start -->
<!-- badges: end -->

The goal of MHplot is to visualise the marginal homogeneity of row and column variables in a square contingency table.

## Installation

You can install the development version of MHplot from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SShinodaPhD/MHplot")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(MHplot)

## basic example of a sqare contingency table
mat426 <- matrix(c(
	 0, 30,  30, 30,
	10,  0,  30, 30,
	10, 10,   0,  0,
	10, 10, 160,  0
),4,4,byrow=T)
```

If legend is FALSE, the estimate of measure and 95% confidence intervals are not displayed (default).

```{r}
MHplot(mat=mat426, legend = FALSE)
```

If legend is TRUE, the estimate of measure and 95% confidence intervals are displayed.

```{r}
MHplot(mat=mat426, legend = TRUE)
```

